Behavior Driven Development in Haskell

### 2012-06-01 paper.tex
BCP: Step 4, conclusion: wording

\noindent Our implementation already fulfils this spec, so we are
fine. Some time later however, the one person in our team that knows
more about Haskell than we do, convinces us that throwing exceptions
from pure code is considered poor design. Hence, we change the
specification so that zero should be the result for negative inputs.

@@

\noindent In fact, it is the case that fib returns 0 for all negative
numbers.

@@

\noindent This concludes our example coding session.  We have seen how
to utilize behavior driven development to incrementally build a small
library.  We always extend or adapt the specification first, watch it
fail,  and then fix the implementation.  The combinators {\tt
shouldBe}, {\tt shouldReturn} and {\tt shouldThrow} can be used to
specify behavior of functions in an intuitive, easy to read manner.

>>>>

\noindent Our implementation already fulfils this spec, so we are
fine. Some time later however, the one person in our team that knows
more about Haskell than we do, convinces us that throwing exceptions
from pure code is considered poor design. Hence, we change the
specification so that negative inputs should have zero as result.

@@

\noindent In fact, should be the case that fib returns 0 for all
negative numbers.

@@

\noindent Again, our implementation already fulfils that spec.

This concludes our example coding session.  We have seen how to utilize
behavior driven development to incrementally build a small library.
We always extend or adapt the specification first, watch it fail,  and
then tighten the implementation.  The combinators {\tt shouldBe}, {\tt
shouldReturn} and {\tt shouldThrow} can be used to specify behavior of
functions in an intuitive, easy to read manner.
